\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=1.25in]{geometry}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{palatino}
\usepackage{tipa}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
 
\pagestyle{fancy}
\fancyhf{}
\lhead{Nathaniel T. Stemen}
\rhead{University of Washington}

\lfoot{Assistantship and Fellowship Application}
\rfoot{Page \thepage}

\begin{document}

\section*{Citizenship/Visa status}

US citizen

\section*{Have you applied for/received funding to attend the University of Washington from any grants or fellowship organization?}

I have not.

\section*{Do you have any previous teaching, tutoring, or teaching assistant (TA) experience?} 

For nearly two years I worked as a mathematics tutor working at a college prep academy where I acted as a teaching assistant, helping students in class with assignments and homework. I helped in Algebra, Algebra II, Pre-Calc, and Calculus courses to help understands core concepts and apply that knowledge to solve problems. In the summer of 2016, I was also given the opportunity to teach a Pre-Calculus course of roughly 10 students aimed at helping them prepare for A.P.\ courses the following year. Here I was in charge of creating and grading all assignments and resources. This experience showed me how fun, and meaningful teaching can be, and how important it is to the mathematics community. Without passionate teachers, students rarely find the energy to dive deep into fascinating areas of mathematics. I tried to encourage this by relating the mathematics we were learning to topics the students were interested in such as biology, cycling, and even aviation.

\section*{Do you have any previous research experience? Any publications (including in-progress, submitted, or in print)?}

For two summers I worked at Yale University on an experiment searching for a hypothetical sterile neutrino. While there, we published two papers, and I presented a poster at a national physics conference. Also at Overleaf (my current employer), I am working with multiple others (from Overleaf and other organizations) to write a report on how scientific  collaboration across countries and institutions happens, and the degree to which it happens. On this project I am responsible for collecting data and will also be writing portions of the report. The report is expected to be published by Digital Science.

\section*{List any honors awarded to you for scholarship (fellowships, prizes, etc.).}

\begin{itemize}
    \item University Honors Scholar
    \item Sigma Pi Sigma inductee (physics honors society)
\end{itemize}

\section*{What computer software are you familiar with, and at what level (beginner, intermediate, expert)?}

% \begin{center}
\begin{tabular}{lrl}
    Category &  & Expertise \\ \toprule
    Operator System & MacOS & expert \\
     & Linux & intermediate \\
    Programming Language & python & expert \\
     & javascript & expert \\
     & SQL & expert \\
     & \LaTeX{} & expert \\
     & HTML/CSS & intermediate \\
     & Mathematica & beginner \\
     & Matlab & beginner \\
     & C++ & beginner \\
    Software Tools & git & expert \\
     & bash & intermediate
\end{tabular}
% \end{center}

\section*{What is your present position/activity?}

Currently I am employed by Overleaf (\href{https:www.overleaf.com}{\texttt{overleaf.com}}) where I work as a full-time remote software developer. With a team that is over 3,000 miles away (in London), it is important that I maintain a strong work ethic and am able to get work done on my own without immediate oversight/guidance. I believe these are skills that will help me tremendously with the work required with my graduate studies and work.

\end{document}